Response to the defense feedback

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

During the evolution of the computer architecture, researchers found that CPUs process data much faster than the main memory (DRAM) can supply. As a result, CPUs adopted a hierarchy memory architecture to bridge the performance gap between the CPU and the main memory. By caching extra copies of recently accessed data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.

>>>>

During the evolution of the computer architecture, researchers found that CPUs process data much faster than the main memory (DRAM) can supply. As a result, CPUs adopted a hierarchy memory architecture to bridge the performance gap between the CPU and the main memory. By caching extra copies of recently accessed data and code in a smaller but faster memory, the CPU can get its most recently accessed code and data in a shorter time.
